Postdoctoral Researcher

### 2017-08-11 GenericCV/PostdocCSU/CV_Shih-Kai_Lin.tex
Add publications and honors.

\name{Shih-Kai}{Lin}
\title{Postdoctoral Researcher}
\address{1700 W Plum St Apt 53E}{Fort Collins, CO, 80521}
\phone[mobile]{+1~(832)~907~9035}
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{Shihkai.Lin@colostate.edu}
%\homepage{www.johndoe.com}
\social[linkedin]{shihkailin}
%\social[twitter]{jdoe}
%\social[github]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
\quote{}

@@

\section{Honors and Professional Memberships}
\cvitem{Nov 2015}{The 2016 Breakthrough Prize in Fundamental Physics}
\cvitem{Mar 2013}{American Physical Society}
\cvitem{Nov 2009}{Golden Key International Honour Society}
\cvitem{2005}{Government Fellowship for Studying Abroad from Ministry of Education, Taiwan}

@@

\section{Publications}
\cvitem{2016}{(Daya Bay Collaboration), ``Measurement of the Reactor Antineutrino Flux and Spectrum at Daya Bay", \textit{Phys. Rev. Lett.} 116, 061801 (2016)}

\cvitem{2015}{(Daya Bay Collaboration), ``New Measurement of Antineutrino Oscillation with the Full Detector Configuration at Daya Bay", \textit{Phys. Rev. Lett.} 115, 111802 (2015)}

\cvitem{2013}{Z. Ning, Q.M. Zhang, J.L. Xu, L. Lebanowski, J.W. Zhang, C.G. Yang, M. He, J. Zhao, J.H. Zou, V. P{\v e}{\v c}, \underline{\textbf{\emph{Sh.-K. Lin}}}, M.Y. Guan, H.F. Hao, L. Zheng, X.L. Ji, F. Li, K. Lau and V. Vorobel, ``Calibration algorithms of RPC detectors at Daya Bay Neutrino Experiment", \textit{JINST} 8 (2013) T03007}

@@

\cvitem{2011}{XU Ji-Lei, GUAN Meng-Yun, YANG Chang-Gen, WANG Yi-Fang, ZHANG Jia-Wen, LU Chang-Guo, Kirk McDonald, Robert Hackenburg, Kwong Lau, Logan Lebanowski, Cullen Newsom, \underline{\textbf{\emph{Lin Shih-Kai}}}, Jonathan Link, MA Lie-Hua, Viktor P{\v e}{\v c}, Vit Vorobel, CHEN Jin, LIU Jin-Chang, ZHOU Yong-Zhao, LIANG Hao, ``Design and preliminary test results of Daya Bay RPC modules", \textit{Chinese Phys. C} 35(9): 844-850}

@@

\cvitem{2010}{M. Deniz, S.T. Lin, V. Singh, J. Li, H.T. Wong, S. Bilmis, C.Y. Chang, H.M. Chang, W.C. Chang, C.P. Chen, M.H. Chou, K.J. Dong, J.M. Fang, C.H. Hu, G.C. Jon, W.S. Kuo, W.P. Lai, F.S. Lee, S.C. Lee, H.B. Li, H.Y. Liao, C.W. Lin, F.K. Lin, \underline{\textbf{\emph{S.K. Lin}}}, Y. Liu, J.F. Qiu, M. Serin, H.Y. Sheng, L. Singh, R.F. Su, W.S. Tong, J.J. Wang, P.L. Wang, S.C. Wu, S.W. Yang, C.X. Yu, Q. Yue, M. Zeyrek, D.X. Zhao, Z.Y. Zhou, Y.F. Zhu, and B.A. Zhuang, ``Measurement of $\bar{\nu}_e$-elelctron cross section with a CsI(Tl) scintillating crystal array at the Kuo-Sheng nuclear power reactor", \textit{Phys. Rev. D} 81, 072001 (2010)}

@@

\cvitem{2008}{H Y Liao, H M Chang, M H Chou, M Deniz, H X Huang, F S Lee, H B Li, J Li, C W Lin, F K Lin, \underline{\textbf{\emph{S K Lin}}}, S T Lin, V Singh, H T Wong and S C Wu, ``Production and decay of the $^{73}$Ge*(1/2$^-$) metastable state in a low-background germanium detector", \textit{J. Phys. G: Nucl. Part. Phys.} 35 (2008) 077001}

>>>>

\name{Shih-Kai}{Lin}
\title{Postdoctoral Researcher}
\address{2247 Oakridge Dr Apt 1}{Aurora, IL, 60502}
\phone[mobile]{+1~(864)~349~5588}
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{Shihkai.Lin@colostate.edu}
%\homepage{www.johndoe.com}
\social[linkedin]{shihkailin}
%\social[twitter]{jdoe}
%\social[github]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
\quote{}

@@

\section{Honors and Professional Memberships}
\cvitem{Nov 2016}{Fermi National Accelerator Laboratory \href{http://npc.fnal.gov/fall-2016-npc-scholars/}{Fall 2016 NPC Scholars}}
\cvitem{Nov 2015}{The 2016 Breakthrough Prize in Fundamental Physics}
\cvitem{Mar 2013}{American Physical Society}
\cvitem{Nov 2009}{Golden Key International Honour Society}
\cvitem{2005}{Government Fellowship for Studying Abroad from Ministry of Education, Taiwan}

@@

\section{Publications}
\cvitem{2017}{(NOvA Collaboration), ``Constraints on oscillation parameters from $\nu_e$ appearance and $\nu_\mu$ disappearance in NOvA'', \textit{Physical Review Letters} 118 (23), 231801}

\cvitem{2017}{(NOvA Collaboration), ``Measurement of the Neutrino Mixing Angle $\theta_{23}$ in NOvA'', \textit{Physical Review Letters} 118 (15), 151802}

\cvitem{2017}{(Daya Bay Collaboration), ``Measurement of electron antineutrino oscillation based on 1230 days of operation of the Daya Bay experiment'', \textit{Physical Review D} 95 (7), 072006}

\cvitem{2017}{(Daya Bay Collaboration), ``Improved measurement of the reactor antineutrino flux and spectrum at Daya Bay'', \textit{Chinese Physics C} 41 (1), 013002}

\cvitem{2016}{(Daya Bay Collaboration and MINOS Collaboration), ``Limits on active to sterile neutrino oscillations from disappearance searches in the MINOS, Daya Bay, and Bugey-3 experiments'', \textit{Physical Review Letters} 117 (15), 151801}

\cvitem{2016}{(Daya Bay Collaboration), ``Improved search for a light sterile neutrino with the full configuration of the Daya Bay experiment'', \textit{Physical Review Letters} 117 (15), 151802}

\cvitem{2016}{(Daya Bay Collaboration), ``New measurement of $\theta_{13}$ via neutron capture on hydrogen at Daya Bay'', \textit{Physical Review D} 93 (7), 072011}

\cvitem{2016}{(Daya Bay Collaboration), ``The detector system of the Daya Bay reactor neutrino experiment'', \textit{Nuclear Instruments and Methods in Physics Research A} 811 (2016) 133-161}

\cvitem{2016}{(Daya Bay Collaboration), ``Measurement of the Reactor Antineutrino Flux and Spectrum at Daya Bay'', \textit{Phys. Rev. Lett.} 116, 061801 (2016)}

\cvitem{2015}{(Daya Bay Collaboration), ``New Measurement of Antineutrino Oscillation with the Full Detector Configuration at Daya Bay'', \textit{Phys. Rev. Lett.} 115, 111802 (2015)}

\cvitem{2015}{(Ken Chow, John Cummings, Emily Edwards, William Edwards, Ry Ely, Matthew Hoff, Logan Lebanowski , Bo Li, Piyi Li, \underline{\textbf{\emph{Shih-Kai Lin}}}, Dawei Liu, Jinchang Liu, Kam-Biu Luk, Jiayuan Miao, Jim Napolitano, Juan Pedro Ochoa-Ricoux, Jen-Chieh Peng, Ming Qi, Herbert Steiner, Paul Stoler, Mary Stuart, Lingyu Wang, Changgen Yang, Weili Zhong), ``Waterproofed photomultiplier tube assemblies for the Daya Bay reactor neutrino experiment'', \textit{Nuclear Instruments and Methods in Physics Research A} 794 (2015) 25-32}

\cvitem{2015}{(Daya Bay Collaboration), ``The muon system of the Daya Bay Reactor antineutrino experiment'', \textit{Nuclear Instruments and Methods in Physics Research A} 773 (2015) 8-20}

\cvitem{2013}{Z. Ning, Q.M. Zhang, J.L. Xu, L. Lebanowski, J.W. Zhang, C.G. Yang, M. He, J. Zhao, J.H. Zou, V. P{\v e}{\v c}, \underline{\textbf{\emph{Sh.-K. Lin}}}, M.Y. Guan, H.F. Hao, L. Zheng, X.L. Ji, F. Li, K. Lau and V. Vorobel, ``Calibration algorithms of RPC detectors at Daya Bay Neutrino Experiment'', \textit{JINST} 8 (2013) T03007}

@@

\cvitem{2011}{XU Ji-Lei, GUAN Meng-Yun, YANG Chang-Gen, WANG Yi-Fang, ZHANG Jia-Wen, LU Chang-Guo, Kirk McDonald, Robert Hackenburg, Kwong Lau, Logan Lebanowski, Cullen Newsom, \underline{\textbf{\emph{Lin Shih-Kai}}}, Jonathan Link, MA Lie-Hua, Viktor P{\v e}{\v c}, Vit Vorobel, CHEN Jin, LIU Jin-Chang, ZHOU Yong-Zhao, LIANG Hao, ``Design and preliminary test results of Daya Bay RPC modules'', \textit{Chinese Phys. C} 35(9): 844-850}

@@

\cvitem{2010}{M. Deniz, S.T. Lin, V. Singh, J. Li, H.T. Wong, S. Bilmis, C.Y. Chang, H.M. Chang, W.C. Chang, C.P. Chen, M.H. Chou, K.J. Dong, J.M. Fang, C.H. Hu, G.C. Jon, W.S. Kuo, W.P. Lai, F.S. Lee, S.C. Lee, H.B. Li, H.Y. Liao, C.W. Lin, F.K. Lin, \underline{\textbf{\emph{S.K. Lin}}}, Y. Liu, J.F. Qiu, M. Serin, H.Y. Sheng, L. Singh, R.F. Su, W.S. Tong, J.J. Wang, P.L. Wang, S.C. Wu, S.W. Yang, C.X. Yu, Q. Yue, M. Zeyrek, D.X. Zhao, Z.Y. Zhou, Y.F. Zhu, and B.A. Zhuang, ``Measurement of $\bar{\nu}_e$-elelctron cross section with a CsI(Tl) scintillating crystal array at the Kuo-Sheng nuclear power reactor'', \textit{Phys. Rev. D} 81, 072001 (2010)}

@@

\cvitem{2008}{H Y Liao, H M Chang, M H Chou, M Deniz, H X Huang, F S Lee, H B Li, J Li, C W Lin, F K Lin, \underline{\textbf{\emph{S K Lin}}}, S T Lin, V Singh, H T Wong and S C Wu, ``Production and decay of the $^{73}$Ge*(1/2$^-$) metastable state in a low-background germanium detector'', \textit{J. Phys. G: Nucl. Part. Phys.} 35 (2008) 077001}
